\documentclass [letterpaper,11pt]{article}
\usepackage{fullpage,amsmath}
\usepackage[hidelinks]{hyperref}

\newcommand{\urlnofont}[1]{\urlstyle{same}\url{#1}}

\begin{document}

\begin{center}
\Large Additional Course Policies
\end{center}

\begin{description}

\item[Access and Accommodations:]
Your experience in this class is important to me.  If you anticipate or experience physical or academic barriers based on disability, please let me know immediately so we can discuss options.  If you have already established accommodations with Student Accessibility Services (SAS), please communicate your approved accommodations to me at your earliest convenience so we can discuss your needs in this course.

If you have not yet established services through SAS, but have a condition that requires accommodations (conditions include but not limited to mental health, attention-related, learning, vision, hearing, physical or chronic health), please contact SAS at 901-843-3885, Burrow Hall 4th floor, or by visiting  \texttt{www.rhodes.edu/accessibility}.

Specific logistics for extended time or distraction-limited testing environments should be arranged with the instructor 
at least one week prior to the exam during which they 
will be used.

  \item[Academic Integrity:]
   Plagiarism, cheating, and similar anti-intellectual behavior are serious violations of academic ethics and will be correspondingly penalized. If you are concerned about a possible violation of this kind, please talk with me.  I understand that being a student at Rhodes 
can be stressful sometimes and you will have many demands on your time.  However, I would
much rather have you turn in a partially-completed assignment or do poorly on a test than
have you violate the Rhodes Honor Code.  I can --- and very much want to --- help you if you don't understand the material, but violations of academic integrity will be dealt with harshly.
   
Unless otherwise specified, everything you submit in this course must be your own work and represent
your individual effort.  These are all included in the definition of reportable Honor Code violations for this course:
copying all or part of a solution to a problem, 
downloading a solution from the internet and submitting it as your own, using artificial intelligence tools (such as ChatGPT) to generate solutions,
having someone else provide the solution for you, or allowing someone else to copy from you.    If you have any doubt about what type of behavior is acceptable, please talk with me.

\item[Diversity:]
A diverse learning community is a necessary element of a liberal arts education, for self-understanding is dependent upon the understanding of others. 
We are committed to fostering a community in which diversity is valued and welcomed. To that end any discrimination or 
harassment on the basis of race, gender, color, age, religion, disability, sexual orientation, gender identity or expression, genetic information, and national or ethnic origin, will not be tolerated in the classroom.

We are committed to providing an open learning environment. Freedom of thought, a civil exchange of ideas, and an appreciation of diverse perspectives are fundamental characteristics of a community that is committed to critical inquiry. To promote such an academic and social environment we expect integrity and honesty in our relationships with each other and openness to learning about and experiencing cultural diversity. We believe that these qualities are crucial to fostering social and intellectual maturity and personal growth.

Intellectual maturity also requires individual struggle with unfamiliar ideas. We recognize that our views and convictions will be challenged, and we expect this challenge to take place in a climate of open-mindedness and mutual respect.

\item[Sexual Misconduct Disclosure:]
Rhodes is committed to ensuring a safe learning environment that supports the dignity of all members of the Rhodes community. Rhodes prohibits and will not tolerate sexual misconduct, which includes, but is not limited to, dating/domestic violence, sexual assault, sexual exploitation, stalking, sexual harassment and sex/gender discrimination. Rhodes strongly encourages members of the Rhodes community to report instances of sexual misconduct immediately.  All Rhodes faculty, staff, Peer Advocates, and Resident Assistants are Mandatory Reporters (exceptions are confidential resources: Counseling Center, Chaplain, and Student Health Center) and are required by the College to report any knowledge they receive of possible violations of this policy to the Title IX Coordinator.  If you choose to share information related to sexual misconduct with me, I will report it to the Title IX Coordinator; however, you will control how your report is handled and you are not required to pursue a formal claim.  The goal is to make you aware of the range of options and resources that are available to you.  For more information about Rhodes' sexual misconduct policy or to make a report please see \texttt{www.rhodes.edu/titleix}.

\item \textbf{Unauthorized Recording or Distribution of Classroom Proceedings}: Students are not permitted to record or distribute classroom lectures or discussions without either the express written approval of the faculty member teaching the course or an accommodation through Student Accessibility Services. Qualified students with disabilities that impact their ability to take or read notes should have already received an accommodation through Student Accessibility Services that permits them to record lectures. If Student Accessibility Services has determined that recording lectures and classroom discussions is an appropriate accommodation, the recording may be used only for personal academic purposes. Authorized student-initiated recording must not be made available to anyone outside of the students enrolled in the class in any fashion, including posting online, sending by email, or distributing through other media without the express written consent of the faculty member responsible for the course. Unauthorized recording or dissemination of recorded classroom proceedings, including distribution for compensation, is strictly prohibited and is a violation of the Rhodes Honor Code.



\end{description}


\end{document}


























